---
name: Matthew
surname: Kusen
position: "Demography - Public Health - Data Analysis"
address: "Bangkok, Thailand"
phone: +66 91 792 8610
email: "mrkusen@gmail.com"
www: kusen.netlify.app
twitter: mkusen
github: mrkusen
linkedin: mrkusen
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(tibble)
library(glue)


```

# Overview

* Specialist in Sexual and Reproductive Health (SRH) and Gender-Based Violence (GBV) programming with over seven years of experience managing humanitarian and development initiatives in Asia and the Pacific. Expertise in applying MISP standards, leading management and design in SRH programs, and fostering dymanic and results-driven partnerships.

```{r}
#input data


## Skills
skills <- read_csv(here::here("data", "skills.csv")) %>% 
  group_by(category) %>% 
  mutate(skill = paste(skill, collapse = ", ")) %>% 
  ungroup %>% 
  unique

## Jobs
jobs <- read_csv(here::here("data", "jobs.csv"))
jobs = as_tibble(jobs)
```

# Employment



```{r}
jobs %>%
  detailed_entries(
    with = role,
    what = company,
    why = details,
    when = glue::glue("{startMonth} {startYear} --> {endMonth} {endYear}",.na = ""),
    where = where
  )

```




# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Arts in Demography", "December 2022", "Chulalongkorn University", "Bangkok, Thailand",
  "Bachelor of Political Science", "May 2012", "University at Buffalo, SUNY", "New York, USA",
  "Exchange Student", "2011", "Université de Paris 7", "Paris, France"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Skills

```{r}
skills %>% 
  detailed_entries(what = skill, with = category)
```



# Publications

```{r}
library(dplyr)

bibliography_entries("/Users/matthew/Documents/Career/Resume/Kusen_CV/kusen_publications.bib") %>%
  arrange(desc(issued$family), issued)
```

# Training

```{r}
tribble(
  ~Year, ~Type, ~Place,
  2022, "Python Fundamentals Track - DataCamp", "online",
  2019, "Monitoring & Evaluation for Results - IMA International", "Bangkok, Thailand",
  2018, "Hostile Environment Awareness Training (HEAT) - Human Development Forum Foundation","Thailand",
  2018, "CPR and First Aid Training - First Aid Bangkok", "Thailand",
  2017, "Rape Crisis Counsellor Training - Department of Health ", "New York, USA",
  2016, "Trainer of Clinical Care for Sexual Assault Survivors (CCSAS) - International Rescue Committee", "Uganda",
  2014, "Minimum Initial Service Package (MISP) for Reproductive Health In Crisis - IAWG", "online"
) %>%  
  brief_entries(
    Type,
    Year, 
    Place
  )
```


# Volunteer & Related Experience

```{r}
tribble(
  ~Year, ~Type, ~Place,
  "2015-2017", "Activist Council - Planned Parenthood of New York", "NYC, USA",
  "2016-2017", "Community Activist - Anti-Violence Project of New York", "NYC, USA",
  "2011-2012", "English Instructor -  École pour l'informatique et les nouvelles technologies (EPITECH)", "Paris, France",
  "2011-2011", "Volunteer - Peace & Tolerance Program, Action Aid Denamrk", "Denmark",
) %>%  
  brief_entries(
    Type,
    Year, 
    Place
  )
```

# Country Experience
Ukraine, Indonesia, Philippines, Fiji, Papua New Guinea, Haiti, Central African Republic (CAR), Democratic Republic of the Congo (DRC), Togo, Sierra Leone, United States, Thailand, Bhutan, Sri Lanka, Poland and France



```{r}
#Insert Map

#load packages
library(tidyverse)
library(rvest)
library(magrittr)
library(ggmap)
library(stringr)
library(tidyverse)
library(sf)

#update country experience list and country support list
country_w <- c("Ukraine","Poland","Indonesia","Philippines","Fiji",
"Papua New Guinea","Haiti", "Central African Republic", "Democratic Republic of the Congo", "Togo", "Sierra Leone", "USA", "Thailand","France","Denmark","Bhutan","Sri Lanka","Mongolia")
country_work <- cbind(country_w,"worked")

country_s <- c("Nigeria","Chad","Burkina Faso","Niger","Ghana","South Sudan","Tanzania","Afghanistan","Pakistan","India","Bangladesh","Sri Lanka","Myanmar","Syria","Yemen","Uganda","Malaysia","Kenya")
country_support <- cbind(country_s,"support")

country_list_CV <- rbind(country_work,country_support) %>% as_tibble()
country_list_CV <- rename(country_list_CV, country = country_w,
       type = V2)

#load map data
map.world <- map_data("world")
#remove Antarctica
map.world <- map.world %>% filter(region != "Antarctica")

#verify all countries found in world map
check <- map.world %>% filter(region %in% country_list_CV$country)
checked <- unique(as.character(check$region))
# checked
# dim(country_list_CV)

#join
map.world_joined <- left_join(map.world, country_list_CV, by = c('region' = 'country'))

# flag the countries to be filled in for worked in and supported remotely

plot_work_experience <- ggplot() +
    geom_polygon(data = map.world_joined, 
                 aes(x = long, y = lat, group = group,
                     fill = type))+
    theme(axis.ticks = element_blank(),axis.text = element_blank(),
          axis.title = element_blank(),panel.grid = element_blank(),
          legend.position = c(.15,.3),
          plot.background = element_rect(fill = "#FFFFFF"),
          panel.background = element_rect(fill = "#FFFFFF"))+
    labs(fill="Country Experience")+
    scale_fill_discrete(name="Country Experience", 
                      labels=c("Supported Remotely",
                               "Worked In-Country"," "),
                      na.value="grey",
                      type = c('cadetblue3','darkorchid1'))
plot_work_experience
```

map created with ggmap http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf

CV created using RMarkdown in RStudio. Reproducible code and data can be found at https://github.com/mrkusen/Kusen_CV